\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\geometry{a4paper, margin=1in}

\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}

\begin{document}

% Header
\begin{center}
    \textbf{\Huge Stefan Stafie} \\[0.5em]
    \textbf{Software Developer / System Engineer} \\[0.5em]
    \href{mailto:stefanstafie99@gmail.com}{stefanstafie99@gmail.com} \textbullet{} \href{https://www.linkedin.com/in/stefan-stafie-baa66a120}{LinkedIn: stefan-stafie-baa66a120} \textbullet{} \href{https://github.com/StefanStafie}{GitHub: StefanStafie}
\end{center}

\hrule
\vspace{1em}

% About Me
\section*{About Me}
I am a software developer with specialized studies in computer science and a strong focus on building maintainable, scalable software. Over the last 4+ years at Continental, I have contributed to cross-functional teams delivering high-quality features in safety-critical and high-uptime environments. 

I enjoy designing clear interfaces, automating repetitive work, and improving engineering processes. Outside of work, I create useful applications for personal use.

\vspace{1em}

% Skills
\section*{Skills}
\textbf{Backend Development:} C\#, ASP.NET, REST API, SQL, Design Patterns \\
\textbf{Scripting \& Programming:} .NET Framework applications, C++, Ps1, Batch \\
\textbf{Versioning \& Collaboration:} Git/SVN, CI/CD (GitHub Actions), Code Review, Clean Code \\
\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, Performance Analysis, Vulnerability Scanning \\
\textbf{Methodologies \& Workflow:} Agile, Confluence, KPI Tracking

\vspace{1em}

% Experience
\section*{Software Developer — Continental}
\textit{2021 — Present · Iasi, Romania} 
\begin{itemize}[leftmargin=*]
    \item Built Windows applications for running fully automated qualification tests. Use of test engines, databases, thread-safe logging, and dynamic libraries load.
    \item Developed Windows applications for managing multiple shopfloor computers. Features such as remote access and management tools were integrated.
    \item Built automated test pipelines (CI/CD) and maintained underlying servers and services.
    \item Collaborated with cross-functional international teams.
    \item Maintained legacy code and extended it with new features.
    \item Configure hardware devices and implement communication via drivers.
\end{itemize}

\section*{Masters of Information Systems in Business}
\textit{UAIC - FEAA, Iasi} 
\begin{itemize}[leftmargin=*]
    \item Advanced knowledge of distributed database systems, SQL and NoSQL.
    \item Project management and team management.
    \item Support systems for business intelligence.
\end{itemize}

\section*{Bachelors of Computer Science}
\textit{UAIC - FII, Iasi} 
\begin{itemize}[leftmargin=*]
    \item Data structures, Algorithms, OOP.
    \item Distributed Systems, Cloud Computing and Internet of Things.
    \item Machine learning, Neural Networks and Artificial Intelligence.
    \item Performance driven programming and Software Efficiency.
    \item Video Game and UI Design
\end{itemize}

\vspace{1em}

% Projects
\section*{Personal projects}
\textbf{Remote PC Control (C\#)} \\
A Windows service-based application allowing remote connection and control of PCs via IP.  Takes full advantage of image processing and TCP communication.

\textbf{Machine Learning and AI Projects (Python)} \\
Implemented projects focused on finding patterns in images or data to classify new images or predict features of new data.

\textbf{Server-Based Coin Management Site (PHP)} \\
Developed a site for numismatic purposes, enabling CRUD operations for coins, basic search, filtering, and data export, similar to store websites.

\textbf{Console Projects (C++)} \\
Created applications such as hotel reservation systems, offline messengers, and Kahoot-style quiz applications with multi-threaded server-client interactions.

\textbf{Microcontroller Programming (C)} \\
Worked on automotive microcontroller applications, handling event-based sensors, digital outputs, and displays.

\textbf{Tic Tac Toe Server and Gomoku (Java)} \\
Implemented classic games with GUI in Java and REST API functionality for Tic Tac Toe.

\end{document}
